The Asteroseismic Imprints of Mass Transfer

### 2024-04-07 paper/paper_AA.tex

@@

Asteroseismology probes the internal structure of stars through the analysis of stellar pulsations \citep{Aerts+2010} and so may hold the key to directly probing how accretor stars adjust to gaining mass \citep[e.g.][]{Renzo+2021}. %It is well established that asteroseismology can be used to estimate precise stellar masses, radii and ages based on stellar oscillation modes \citep{Aerts+2010}.
In particular, high-order gravity ($g$) mode pulsations carry information about the deep radiative interiors of stars and the boundary between the convective core and radiative envelope. Main-sequence stars that exhibit $g$-modes include F-type $\gamma$~Doradus stars, driven by convective flux blocking \citep{Guzik+2000} and Slowly Pulsating B-type (SPB) stars, driven by the $\kappa/\gamma$-mechanism \citep{Waelkens+1985, Waelkens+1991, Cox+1992, Pamyatnykh+1999}.
% These pulsators include $\gamma$ Doradus stars driven by the modulation of the radiative flux by convection at the base of a deep envelope convection zone \citep{Guzik+2000}, and Slowly Pulsating B (SPB) stars and $\beta$ Ceph stars driven by the $\kappa$-mechanism \citep{Waelkens+1985, Waelkens+1991, Kiriakidis+1992, Moskalik+1992, Cox+1992}.
These $g$-mode pulsators have been used to provide insights into many aspects of stellar structure and evolution, such as the masses of stellar cores \citep{Johnston+2021, Pedersen+2022} internal mixing processes \citep{Pedersen+2018,Michielsen+2021}, and angular momentum transport \citep{Aerts+2019,Ouazzani2020,Salmon2022,Burssens+2023,Mombarg2023,Moyano2024}. Recent work has also suggested that $g$-modes can be used to probe the binary evolutionary history of stellar mergers in the evolution products of low- and intermediate-mass \citep{Rui+2021} and high-mass stars \citep{Bellinger+2023:2023arXiv231100038B}.

@@

Earlier works have explored the asteroseismic modelling of stars in post mass-transfer binaries, with various degrees of accounting for the history of mass transfer. In particular, \citet{Guo2017b, Guo+2017:2017ApJ...837..114G} and \citet{Chen2021} performed asteroseismic analysis of pulsating stars in post-mass transfer binaries observed by {\it Kepler}. While \citet{Guo2017b,Guo+2017:2017ApJ...837..114G} found suitable solutions using only single star evolution models, \citet{Chen2021} compared solutions from binary and single star evolution models. Although \citet{Guo+2017:2017ApJ...837..114G} briefly mention that their solutions may be impacted by not considering the different composition and $g$-mode cavity resulting from mass transfer, they make no further analysis of these effects. Each of these studies conclude that, for their particular systems, single star models were sufficient.

\citet{Miszuda+2021,Miszuda+2022:2022MNRAS.514..622M} investigated the instability of $p$-modes in two post mass transfer binaries computed with \texttt{MESA}. In their model, the second star accretes nearly conservatively. At the late stages of accretion, the deeper helium-rich layers of the donor star are transferred. The resulting accretor becomes heavily enriched in helium in its outermost layers. They find that this affects overall structure, the mode excitation and pulsation frequencies. In their models, the enriched layer of helium stays is only present at the surface leading to an inversion of average particle mass (mean molecular weight, see their Figure~10). One would expect that mixing processes, such as the Rayleigh-Taylor instability, thermohaline mixing and also rotational mixing \citep{Kippenhahn+1980, Cantiello+2007}, would mix the helium-rich material with the layers below. Both models and observations suggest this overabundance of helium-rich material is erased even before the end of Roche-Lobe overflow \citep{Renzo+2021}.

@@

In particular, the most pertinent settings that we use for this work are as follows: We adopt the \citet{Ledoux+1947} criterion to account for the presence of a chemical gradient when determining the stability of convection. We include semiconvection following \citet{Langer+1983} with a scaled efficiency of $\alpha_{\rm sc}=0.1$. We use exponential core overshooting from \cite{Herwig+2000}, setting $(f, f_0) = (0.01, 0.005)$ \citep{Claret+2017}. We set a minimum diffusive mixing coefficient of $20\,{\rm cm^2 \, s^{-1}}$; this smooths out any numerical discontinuities in the composition gradients and partially accounts for the lack of rotational mixing in our models. We motivate our choice of $20\,{\rm cm^2 \, s^{-1}}$ and highlight the effect of changing the mixing coefficient on our results in Appendix~\ref{app:min_D_mix}. We do not account for any rotation in our models. For more details on the input physics and settings, see Appendix~\ref{app:mesa_inputs}.

@@

The evolution of the donor (starting at D1) initially follows the 4$\,{\rm M_\odot}$ single star track, expanding across the main sequence, exhausting core hydrogen and moving across the Hertzsprung gap. During the expansion on the Hertzsprung gap, at point D2, the donor overflows its Roche-lobe and diverges from the single star track. As it loses mass, it is driven out of thermal equilibrium. It decreases in luminosity as a fraction of the photons produced deep inside are now used to do work to expand the outer layers.  The orbit shrinks slightly at first, but quickly starts to widen \citep{Renzo+2019:2019A&A...624A..66R}. At point D3 the donor star is still transferring mass but it starts to regain thermal equilibrium. At point D4 the donor has lost its entire hydrogen-rich envelope and contracts within its Roche-lobe. It keeps contracting until it ignites helium at the point marked D5, where it resides a compact subdwarf.

@@

In Figure~\ref{fig:BV_profiles} we compare, for the same central hydrogen content, the Brunt–Väisälä frequency profiles for the accretor star model and single star model with the same final mass. Each panel is for the same central hydrogen content as in Figure~\ref{fig:XH_profiles} for a simple comparison. We additionally show the profile as a both a function of mass coordinate and radial coordinate in the two columns.

@@

% \help{It seems like the amplitude argument could be flawed, if this was true would we not only see amplitude differences in regions with phase differences?}

% \tom{From Earl: on the other hand, all the modes touch essentially all parts of the BV profile, so all modes are sensitive at some level to this change}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{paper/figures/age_xc_relation.pdf}
    \caption{A single star model with the same age and $X_c$ as a mass-gainer will underestimate the age. Comparison of the stellar age of our mass-gainer model and $3.5 \, {\rm M_\odot}$ single star model during post-accretion evolution.}
    \label{fig:age-Xc}
\end{figure}

@@

\paragraph{Binary parameters and the treatment of mass transfer} The mass-gainer model that we use was allowed to accrete only 0.5$\,{\rm M_\odot}$ of material. This was partially motivated by the idea that an accretor with rotation is expected to quickly reach critical rotation and prevent further accretion \citep[e.g.][]{Petrovic+2005}, others do argue that accretion is possible even beyond critical rotation \citep{Popham+1991, Paczynski+1991}. The amount of accreted material will likely affect the quantitative results. If the star had accreted significantly more, its new convective core may have further expanded, possibly erasing the chemical composition gradient and thus tracers of mass transfer and its asteroseismic signals. If the star had accreted significantly less, the imprints on the structure would be milder and probably harder to detect.

@@

\paragraph{Rotation} We have limited the scope of our investigations by neglecting rotation in each model. For slow to moderate rotating $g$-mode pulsators, many recent studies only add the effects of rotation at the stage of calculating pulsation frequencies \citep[e.g.][]{Michielsen+2021}. Yet, mass-gainers could reach close-to-critical rotation during mass transfer due to the exchange of angular momentum \citep{Packet+1981, deMink+2013:2013ApJ...764..166D, Renzo+2021}, and this could impact several aspects of our results \citep[e.g.][and references therein]{Aerts+2023:2023arXiv231108453A}. In practice, such high rotation rates are not found in observations and accretors typically have spins that are only 10-40\% of the critical rate (\citealp{Dervisoglu+2010}, see however e.g., \citealp{Zehe+2018:2018AN....339...46Z}), but this may still significantly impact the asteroseismic signatures.

The two dominant effects concern rotational mixing and the shifting of $g$-modes due to the introduction of the Coriolis force. Rotation is expected to enhance internal chemical mixing throughout the star through mechanisms such as shear mixing, dynamical instabilities, and Eddington-Sweet circulation \citep{Maeder2000}. These mechanisms are expected to act in the vicinity of the core as well and thus alter the chemical composition gradient, which is the key difference between the mass-gainer and single star models. By introducing the Coriolis force, rotation actively shifts the periods of $g$-modes \citep{Townsend2003}, introducing a characteristic tilt in the period spacing pattern \citep{Bouabid+2013}. In addition to the effects of modified chemical mixing profile, rotation will further complicate the construction of observed period spacing patterns. However, this does open up the opportunity to investigate the core rotation of stars that have undergone mass transfer, as was done by \citet{Guo2019}. Future work should investigate the role of rotation in modifying these predictions.

@@

@@

\begin{enumerate}
    \setlength\itemsep{1em}
    \item \textbf{Mass transfer produces a distinct asteroseismic imprint}\\Our accretor star model shows a significantly different internal chemical composition gradient \citep[e.g.][]{Renzo+2021}, and hence Brunt–Väisälä frequency\ (see Figures~\ref{fig:XH_profiles}--\ref{fig:BV_profiles}), even though we only consider non-enriched hydrogen being accreted. While \citet{Miszuda+2021} demonstrated that mass transfer impacts the frequencies of $p$ modes in lower mass $\delta$ Scuti type stars, they considered helium enriched materials being accreted. Even when considering only un-enriched material, the modified chemical gradient selectively traps certain $g$-modes and therefore produces a measurably different asteroseismic signal (see Figure~\ref{fig:period_spacing}) compared to an equal mass star that has undergone single star evolution.
    \item {\bf The asteroseismic signature of rejuvenation persists throughout the main-sequence evolution of the mass gainer}\\ At times soon after rejuvenation, there is only a small region of the star with a non-zero chemical composition gradient (e.g.\ Figure~\ref{fig:XH_profiles}c). Therefore, fewer modes are shifted by the steep chemical gradient. As the star evolves and the region with a non-zero chemical gradient increases, more modes are trapped by the gradient, and even though mixing modifies the remaining gradient, it is present until the terminal-age main sequence. As such, we can see that the differences in the period-spacing patterns of the mass-gainer and single star persist until the end of the main sequence as well. In particular, we notice that the mass gainer has increased oscillatory amplitude in the period-spacing pattern compared to the single star, likely due to the steeper gradient feature.
    % Hence, modes which are trapped in the accretor model show significant differences in their period-spacing patterns when compared to patterns from models that have undergone single star evolution.
    \item {\bf Single-star models cannot robustly reproduce period spacing patterns from mass accreting models}\\We demonstrate that, given realistic observational uncertainties on pulsation period-spacing patterns, we cannot uniquely identify the matching accretor model when using a single-star evolution model (Figure~\ref{fig:chi2}). While the individual maximum a-posteriori point estimates correctly identifies the stellar mass and $X_c$ in many cases, the range of models that are statistically valid covers a much wider parameter range in all cases (Figure~\ref{fig:relative_estimates_psp}). Moreover, even models that correctly estimate mass and $X_c$ significantly underestimate the stellar age (Figure~\ref{fig:age-Xc}).

    \item {\bf The asteroseismic signature of rejuvenation can be identified with detailed modelling} \\
    While we have demonstrated that single star models are able to recover the bulk properties of mass gaining models, there is still clear structure in the period-spacing patterns that can be modelled. As accretor stars are necessarily in binary systems, this provides a unique opportunity to leverage the high-precision fundamental stellar parameter estimates $(<1\%)$ in the asteroseismic modelling procedure \citep[e.g.][]{Torres2010,Johnston2019a,Sekaran2021}. With an independent and precise estimate of the mass gainer stars mass, radius, and age, the asteroseismic analysis will be driven by small difference in the trapping pattern as opposed to matching the asymptotic pattern value \citep{Johnston2019b}. Fortuitously, there are numerous examples of stars that have undergone mass transfer in eclipsing binaries at all masses. 
    % \item \textbf{It is critical to consider full posterior distributions when fitting a mass-gainer}\\We show that, if one considers only the best fitting model, one may infer inaccurate stellar properties when fitting the period spacing pattern of a star that has undergone accretion (see Figure~\ref{fig:chi2}). For our mass-gainer model we find that, though the best-fitting model can be inaccurate, a single star model with the same values of $X_c$ and $M$ remains statistically compatible throughout the post-accretion evolution.
\end{enumerate}
This work demonstrates that asteroseismology can be used to probe the structural impact of mass accretion in binary interaction. These results have immediate implications as this opens the door to providing observational constraints on poorly-understood binary evolution processes that are otherwise unobservable. In particular, there are several classes of known or strongly favoured post-mass transfer systems, such as Algol variables \citep[e.g. ][]{Shi2022} and Be-type stars \citep[e.g.][]{Baade1982,Bodensteiner+2020,LabadieBartz2022}, that are: i) known $g$-mode pulsators, and ii) have existing long time-base photometry with telescopes such as Kepler \citep{Borucki+2010} and TESS \citep{Ricker+2015}. Future work will investigate the sensitivity of asteroseismic signals to the rate of mass transfer, as well as the mixing processes that accompany mass transfer. Finally, detecting the signatures of mass transfer in currently available asteroseismic data will bridge the exploits of asteroseismology to help calibrate predictions of gravitational wave progenitor populations which require at least one episode of mass transfer in their evolution to interpret the observed distributions of gravitational wave progenitors and events \citep{Abbott+2023,Renzo+2023}.

\begin{acknowledgements}
    We thank the Kavli Foundation and the Max Planck Institute for Astrophysics for supporting the 2023 Kavli Summer Program during which much of this work was completed. In particular, the authors thank Isabel Thapa, Stephen Justham, Mahdieh Schmidt and Pascala Garaud for their incredible efforts in organising this program. TW also thanks UW Subject Library Matthew Parsons for helping to track down the original text of \citet{BVF-vaisala} and Donna Thompson for aiding in listing it on NASA ADS. TW applauds Ruggero Valli for his help, and patience, with setting up \texttt{MESA} on the MPA cluster and sharing the secret commands of \texttt{kinit} and \texttt{aklog}. CJ gratefully acknowledges support from the Netherlands Research School of Astronomy (NOVA). CJ thanks Amadeusz Miszuda for sharing his {\sc mesa} {\sc binary} inlists to help start up this research. RT acknowledges support from NASA grant 80NSSC20K0515.
\end{acknowledgements}

@@

The MESA EOS is a blend of the OPAL \citep{Rogers2002}, SCVH
\citep{Saumon1995}, FreeEOS \citep{Irwin2004}, HELM \citep{Timmes2000},
PC \citep{Potekhin2010}, and Skye \citep{Jermyn2021} EOSes. Radiative opacities are primarily from OPAL \citep{Iglesias1993, Iglesias1996}, with low-temperature data from \citet{Ferguson2005} and the high-temperature, Compton-scattering dominated regime by \citet{Poutanen2017}. Electron conduction opacities are from \citet{Cassisi2007} and \citet{Blouin2020}. Nuclear reaction rates are from JINA REACLIB \citep{Cyburt2010}, NACRE \citep{Angulo1999} and additional tabulated weak reaction rates \citet{Fuller1985, Oda1994, Langanke2000}.  Screening is included via the prescription of \citet{Chugunov2007}. Thermal neutrino loss rates are from \citet{Itoh1996}. Roche lobe radii in binary systems are computed using the fit of
\citet{Eggleton1983}. For accretors we include thermohaline mixing once they finish accretion following \citet{Kippenhahn+1980} with an efficiency of $\alpha_{\rm thm} = 1$. We follow the \citet{Kolb+1990} prescription for the mass transfer rate in Roche lobe overflowing binary systems with an implicit scheme.

>>>>

\newcommand{\referee}[1]{{\bf #1}}

@@

Asteroseismology probes the internal structure of stars through the analysis of stellar pulsations \referee{\citep[e.g.,][and references therein]{Aerts+2010}} and so may hold the key to directly probing how accretor stars adjust to gaining mass \citep[e.g.][]{Renzo+2021}. %It is well established that asteroseismology can be used to estimate precise stellar masses, radii and ages based on stellar oscillation modes \citep{Aerts+2010}.
In particular, high-order gravity ($g$) mode pulsations carry information about the deep radiative interiors of stars and the boundary between the convective core and radiative envelope. Main-sequence stars that exhibit $g$-modes include F-type $\gamma$~Doradus stars, driven by convective flux blocking \citep{Guzik+2000} and Slowly Pulsating B-type (SPB) stars, driven by the $\kappa/\gamma$-mechanism \citep{Waelkens+1985, Waelkens+1991, Cox+1992, Pamyatnykh+1999}.
% These pulsators include $\gamma$ Doradus stars driven by the modulation of the radiative flux by convection at the base of a deep envelope convection zone \citep{Guzik+2000}, and Slowly Pulsating B (SPB) stars and $\beta$ Ceph stars driven by the $\kappa$-mechanism \citep{Waelkens+1985, Waelkens+1991, Kiriakidis+1992, Moskalik+1992, Cox+1992}.
These $g$-mode pulsators have been used to provide insights into many aspects of stellar structure and evolution, such as the masses of stellar cores \citep{Johnston+2021, Pedersen+2022} internal mixing processes \citep{Pedersen+2018,Michielsen+2021}, and angular momentum transport \citep{Aerts+2019,Ouazzani2020,Salmon2022,Burssens+2023,Mombarg2023,Moyano2024}. Recent work has also suggested that $g$-modes can be used to probe the binary evolutionary history of stellar mergers in the evolution products of low- and intermediate-mass \citep{Rui+2021} and high-mass stars \citep{Bellinger+2023:2023arXiv231100038B}.

@@

Earlier works have explored the asteroseismic modelling of stars in post mass-transfer binaries, with various degrees of accounting for the history of mass transfer. In particular, \citet{Guo2017b, Guo+2017:2017ApJ...837..114G} and \citet{Chen2021} performed asteroseismic analysis of pulsating stars in post mass-transfer binaries observed by {\it Kepler}. While \citet{Guo2017b,Guo+2017:2017ApJ...837..114G} found suitable solutions using only single star evolution models, \citet{Chen2021} compared solutions from binary and single star evolution models. Although \citet{Guo+2017:2017ApJ...837..114G} briefly mention that their solutions may be impacted by not considering the different composition and $g$-mode cavity resulting from mass transfer, they make no further analysis of these effects. Each of these studies conclude that, for their particular systems, single star models were sufficient.

\citet{Miszuda+2021,Miszuda+2022:2022MNRAS.514..622M} investigated the instability of $p$-modes in two post mass-transfer binaries computed with \texttt{MESA}. In their model, the second star accretes nearly conservatively. At the late stages of accretion, the deeper helium-rich layers of the donor star are transferred. The resulting accretor becomes heavily enriched in helium in its outermost layers. They find that this affects overall structure, the mode excitation and pulsation frequencies. In their models, the enriched layer of helium is only present at the surface leading to an inversion of average particle mass (mean molecular weight, \referee{see Figure~10 of \citealt{Miszuda+2021}}). One would expect that mixing processes, such as the Rayleigh-Taylor instability, thermohaline mixing and also rotational mixing \citep{Kippenhahn+1980, Cantiello+2007}, would mix the helium-rich material with the layers below. Both models and observations suggest this overabundance of helium-rich material is erased even before the end of Roche-Lobe overflow \citep{Renzo+2021}.

@@

In particular, the most pertinent settings that we use for this work are as follows: We adopt the \citet{Ledoux+1947} criterion to account for the presence of a chemical gradient when determining the stability of convection. We include semiconvection following \citet{Langer+1983} with a scaled efficiency of $\alpha_{\rm sc}=0.1$. We use exponential core overshooting from \cite{Herwig+2000}, setting $(f, f_0) = (0.01, 0.005)$ \citep{Claret+2017}\referee{, where, in terms of pressure scale height, $f$ determines how far beyond the convective core overshooting extends and $f_0$ determines how far back into the core the overshooting starts \citep[see][for more details]{Herwig+2000, Paxton2011}}. We set a minimum diffusive mixing coefficient of $20\,{\rm cm^2 \, s^{-1}}$; this smooths out any numerical discontinuities in the composition gradients and partially accounts for the lack of rotational mixing in our models. We motivate our choice of $20\,{\rm cm^2 \, s^{-1}}$ and highlight the effect of changing the mixing coefficient on our results in Appendix~\ref{app:min_D_mix}. We do not account for any rotation in our models. For more details on the input physics and settings, see Appendix~\ref{app:mesa_inputs}.

@@

The evolution of the donor (starting at D1) initially follows the 4$\,{\rm M_\odot}$ single star track, expanding across the main sequence, exhausting core hydrogen and moving across the Hertzsprung gap. During the expansion on the Hertzsprung gap, at point D2, the donor overflows its Roche-lobe and diverges from the single star track. As it loses mass, it is driven out of thermal equilibrium. It decreases in luminosity as a fraction of the photons produced deep inside are now used to do work to expand the outer layers.  The orbit shrinks slightly at first, but quickly starts to widen \citep{Renzo+2019:2019A&A...624A..66R}. At point D3 the donor star is still transferring mass but it starts to regain thermal equilibrium. At point D4 the donor has lost its entire hydrogen-rich envelope and contracts within its Roche-lobe. It keeps contracting until it ignites helium at the point marked D5, where it resides a compact subdwarf. \referee{As noted in Section~\ref{sec:model_setup}, we limit the accretion onto the companion to $0.5 \, {\rm M_\odot}$. Although the donor continues to transfer mass beyond this point, none of this mass is accreted by the companion. Therefore, after $0.5 \, {\rm M_\odot}$ has been accreted we illustrate the track of the donor with a a grey line given it no longer impacts our accretor model, which is the focus of this work.}

@@

In Figure~\ref{fig:BV_profiles} we compare the Brunt–Väisälä frequency profiles for the accretor star model and single star model with the same final mass. Each panel is for the same central hydrogen content as in Figure~\ref{fig:XH_profiles} for a simple comparison. We additionally show the profile as a both a function of mass coordinate and radial coordinate in the two columns.

@@

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{paper/figures/age_xc_relation.pdf}
    \caption{A single star model with the same mass and $X_c$ as a mass-gainer will underestimate the age. Comparison of the stellar age of our mass-gainer model and $3.5 \, {\rm M_\odot}$ single star model during post-accretion evolution.}
    \label{fig:age-Xc}
\end{figure}

@@

\paragraph{Binary parameters and the treatment of mass transfer} The mass-gainer model that we use was allowed to accrete only 0.5$\,{\rm M_\odot}$ of material. This was partially motivated by the idea that an accretor with rotation is expected to quickly reach critical rotation and prevent further accretion \citep[e.g.][]{Petrovic+2005}, however others do argue that accretion is possible even beyond critical rotation \citep{Popham+1991, Paczynski+1991}. The amount of accreted material will likely affect the quantitative results. If the star had accreted significantly more, its new convective core may have further expanded, possibly erasing the chemical composition gradient and thus tracers of mass transfer and its asteroseismic signals. If the star had accreted significantly less, the imprints on the structure would be milder and probably harder to detect.

@@

\paragraph{Rotation} We have limited the scope of our investigations by neglecting rotation in each model. For slow to moderate rotating $g$-mode pulsators, many recent studies only add the effects of rotation at the stage of calculating pulsation frequencies \citep[e.g.][]{Michielsen+2021}. Yet, mass-gainers could reach close-to-critical rotation during mass transfer due to the exchange of angular momentum \citep{Packet+1981, deMink+2013:2013ApJ...764..166D, Renzo+2021}, and this could impact several aspects of our results\referee{, such as the prevalence of the signature of mass transfer in the chemical composition gradient and observed period spacing patter} \citep[e.g.][and references therein]{Aerts+2023:2023arXiv231108453A}. In practice, such high rotation rates are not found in observations and accretors typically have spins that are only 10-40\% of the critical rate (e.g., \citealp{Dervisoglu+2010}, see however e.g., \citealp{Zehe+2018:2018AN....339...46Z}), but this may still significantly impact the asteroseismic signatures.

The two dominant effects \referee{that could impact our results} concern rotational mixing and the shifting of $g$-modes due to the introduction of the Coriolis force. Rotation is expected to enhance internal chemical mixing throughout the star through mechanisms such as shear mixing, dynamical instabilities, and Eddington-Sweet circulation \citep{Maeder2000}. These mechanisms are expected to act in the vicinity of the core as well and thus alter the chemical composition gradient, which is the key difference between the mass-gainer and single star models. By introducing the Coriolis force, rotation actively shifts the periods of $g$-modes \citep{Townsend2003}, introducing a characteristic tilt in the period spacing pattern \citep{Bouabid+2013}. In addition to the effects of modified chemical mixing profile, rotation will further complicate the construction of observed period spacing patterns. However, this does open up the opportunity to investigate the core rotation of stars that have undergone mass transfer, as was done by \citet{Guo2019}. Future work should investigate the role of rotation in modifying these predictions.

@@

\referee{\paragraph{Non-enrichment of accreted material} In previous works it was suggested that differences in the asteroseismic signals of accretors (compared to single stars) could be attributed to an enrichment of the accretor's outer layers as a result of the accretion of helium-rich material \citep[e.g.][]{Miszuda+2021}. With our models we show that these difference are found even when non-enriched material is accreted, and are in our case a result of changes in the accretor's internal structure due to rejuvenation. This is particularly encouraging given that one would expect that mixing processes, such as the Rayleigh-Taylor instability, thermohaline mixing and also rotational mixing \citep{Kippenhahn+1980, Cantiello+2007}, would quickly mix the helium-rich material with the layers below. Both models and observations suggest this overabundance of helium-rich material is erased even before the end of Roche-Lobe overflow \citep{Renzo+2021}.}

@@

\begin{enumerate}
    \setlength\itemsep{1em}
    \item \textbf{Mass transfer produces a distinct asteroseismic imprint}\\Our accretor star model shows a significantly different internal chemical composition gradient \citep[e.g.][]{Renzo+2021}, and hence Brunt–Väisälä frequency\ (see Figures~\ref{fig:XH_profiles}--\ref{fig:BV_profiles}), even though we only consider non-enriched hydrogen being accreted. While \citet{Miszuda+2021} demonstrated that mass transfer impacts the frequencies of $p$ modes in lower mass $\delta$ Scuti type stars, they considered helium enriched materials being accreted. Even when considering only un-enriched material, the modified chemical gradient selectively traps certain $g$-modes and therefore produces a measurably different asteroseismic signal (see Figure~\ref{fig:period_spacing}) compared to an equal mass star that has undergone single star evolution.
    \item {\bf The asteroseismic signature of rejuvenation persists throughout the main-sequence evolution of the mass gainer}\\ At times soon after rejuvenation, there is only a small region of the star with a non-zero chemical composition gradient (e.g.\ Figure~\ref{fig:XH_profiles}c). Therefore, fewer modes are shifted by the steep chemical gradient. As the star evolves and the region with a non-zero chemical gradient increases, more modes are trapped by the gradient, and even though mixing modifies the remaining gradient, it is present until the terminal-age main sequence. As such, we can see that the differences in the period-spacing patterns of the mass-gainer and single star persist until the end of the main sequence as well. In particular, we notice that the mass gainer has increased oscillatory amplitude in the period-spacing pattern compared to the single star, likely due to the steeper gradient feature.
    % Hence, modes which are trapped in the accretor model show significant differences in their period-spacing patterns when compared to patterns from models that have undergone single star evolution.
    \vspace{1cm}
    \item {\bf Single-star models cannot robustly reproduce period spacing patterns from mass accreting models}\\We demonstrate that, given realistic observational uncertainties on pulsation period-spacing patterns, we cannot uniquely identify the matching accretor model when using a single-star evolution model (Figure~\ref{fig:chi2}). While the individual maximum a-posteriori point estimates correctly identifies the stellar mass and $X_c$ in many cases, the range of models that are statistically valid covers a much wider parameter range in all cases (Figure~\ref{fig:relative_estimates_psp}). Moreover, even models that correctly estimate mass and $X_c$ significantly underestimate the stellar age (Figure~\ref{fig:age-Xc}).

    \item {\bf The asteroseismic signature of rejuvenation can be identified with detailed modelling} \\
    While we have demonstrated that single star models are able to recover the bulk properties of mass gaining models, there is still clear structure in the period-spacing patterns that can be modelled. As accretor stars are necessarily in binary systems, this provides a unique opportunity to leverage the high-precision fundamental stellar parameter estimates $(<1\%)$ in the asteroseismic modelling procedure \citep[e.g.][]{Torres2010,Johnston2019a,Sekaran2021}. With an independent and precise estimate of the mass gainer stars mass, radius, and age, the asteroseismic analysis will be driven by small difference in the trapping pattern as opposed to matching the asymptotic pattern value \citep{Johnston2019b}. Fortuitously, there are numerous examples of stars that have undergone mass transfer in eclipsing binaries at all masses. 
    % \item \textbf{It is critical to consider full posterior distributions when fitting a mass-gainer}\\We show that, if one considers only the best fitting model, one may infer inaccurate stellar properties when fitting the period spacing pattern of a star that has undergone accretion (see Figure~\ref{fig:chi2}). For our mass-gainer model we find that, though the best-fitting model can be inaccurate, a single star model with the same values of $X_c$ and $M$ remains statistically compatible throughout the post-accretion evolution.
\end{enumerate}
This work demonstrates that asteroseismology can be used to probe the structural impact of mass accretion in binary interaction. These results have immediate implications as this opens the door to providing observational constraints on poorly-understood binary evolution processes that are otherwise unobservable. In particular, there are several classes of known or strongly favoured post mass-transfer systems, such as Algol variables \citep[e.g. ][]{Shi2022} and Be-type stars \citep[e.g.][]{Baade1982,Bodensteiner+2020,LabadieBartz2022}, that are: i) known $g$-mode pulsators, and ii) have existing long time-base photometry with telescopes such as Kepler \citep{Borucki+2010} and TESS \citep{Ricker+2015}. Future work will investigate the sensitivity of asteroseismic signals to the rate of mass transfer, as well as the mixing processes that accompany mass transfer. Finally, detecting the signatures of mass transfer in currently available asteroseismic data will bridge the exploits of asteroseismology to help calibrate predictions of gravitational wave progenitor populations which require at least one episode of mass transfer in their evolution to interpret the observed distributions of gravitational wave progenitors and events \citep{Abbott+2023,Renzo+2023}.

\begin{acknowledgements}
    We thank the Kavli Foundation and the Max Planck Institute for Astrophysics for supporting the 2023 Kavli Summer Program during which much of this work was completed. In particular, the authors thank Isabel Thapa, Stephen Justham, Mahdieh Schmidt and Pascala Garaud for their incredible efforts in organising this program. We thank the anonymous referee for reviewing our work and their helpful comments. TW also thanks UW Subject Library Matthew Parsons for helping to track down the original text of \citet{BVF-vaisala} and Donna Thompson for aiding in listing it on NASA ADS. TW applauds Ruggero Valli for his help, and patience, with setting up \texttt{MESA} on the MPA cluster and sharing the secret commands of \texttt{kinit} and \texttt{aklog}. CJ gratefully acknowledges support from the Netherlands Research School of Astronomy (NOVA). CJ thanks Amadeusz Miszuda for sharing his {\sc mesa} {\sc binary} inlists to help start up this research. RT acknowledges support from NASA grant 80NSSC20K0515.
\end{acknowledgements}

@@

The MESA equation of state (EOS) is a blend of the OPAL \citep{Rogers2002}, SCVH
\citep{Saumon1995}, FreeEOS \citep{Irwin2004}, HELM \citep{Timmes2000},
PC \citep{Potekhin2010}, and Skye \citep{Jermyn2021} EOSes. Radiative opacities are primarily from OPAL \citep{Iglesias1993, Iglesias1996}, with low-temperature data from \citet{Ferguson2005} and the high-temperature, Compton-scattering dominated regime by \citet{Poutanen2017}. Electron conduction opacities are from \citet{Cassisi2007} and \citet{Blouin2020}. Nuclear reaction rates are from JINA REACLIB \citep{Cyburt2010}, NACRE \citep{Angulo1999} and additional tabulated weak reaction rates \citep{Fuller1985, Oda1994, Langanke2000}.  Screening is included via the prescription of \citet{Chugunov2007}. Thermal neutrino loss rates are from \citet{Itoh1996}. Roche lobe radii in binary systems are computed using the fit of
\citet{Eggleton1983}. For accretors we include thermohaline mixing once they finish accretion following \citet{Kippenhahn+1980} with an efficiency of $\alpha_{\rm thm} = 1$. We follow the \citet{Kolb+1990} prescription for the mass transfer rate in Roche lobe overflowing binary systems with an implicit scheme.
